\chapter{Conclusion and Future Work}
\label{conclusion}
\section{Conclusion}
In this work, we have tried to automatically detect signs of DR by using deep neural networks, especially convolutional neural networks that are recently become popular in difficult image processing and other machine learning tasks especially with huge amount of data. For this purpose, we train deep neural network by using one of the widely used publicly available datasets, Messidor and test with other public datasets. We apply different preprocessing techniques and run several experiments. Experimental results show that deep learning techniques can be promising in the task of automatic detection of DR, but compared to the literature it must be improved. For some cases we reach 80\% accuracy results and 0.9 area under ROC curve, but this results are only for one dataset.  
\section{Future Work}
We plan to use bigger datasets like Kaggle datasets that we could not use in this work. Using bigger datasets will provide more information and convolutional neural networks can learn more information about the images. We plan to work on different image preprocessing techniques in detail, because our initial findings shown in our experiments tells us that preprocessing techniques can be very important. We will try different neural network architecture, for instance in this work the images used were scaled to 128x128 but we plan to run with higher resolutions. Besides we plan to run our experiments by using GPU, since it gives huge performance gain in time if used. We also plan to not only work on diabetic retinopathy detection but also other eye diseases. 